Geometron: A Geometric Language for Graphical Communication

### 2020-10-14 paper1.tex
white paper for quantum information applications of geometron

\title{Geometron: A Universal Language for Graphical Communication}
\author{Lafe Spietz}

@@

    Glyphs consist of sequences of actions.  They are expressed as strings in the form of base 8 addresses separated by commas, e.g.``0300,0341,0333,0341,''.  Some addresses in the action cube consist of glyphs, which in turn reference other glyphs or actions.  Thus many levels of recursion are possible and used routinely.  This is a huge part of the power of this system over existing graphical systems like Adobe Illustrator.  Adding glyphs to the shape table and using those glyphs is not like just copying and pasting shapes in Illustrator.  It is in fact more like building up cell hierarchy in a electronic layout CAD program.

@@

\caption{Figure 3. Bottom Tablet.  This is split between the bottom part of the printable 7 bit ASCII code and various system actions which control things like cursor position while editing glyphs. }
\end{figure}

@@

\caption{Figure 10. Layers/colors.  These are at addresses 0320 through 0327.}
\end{figure}

@@

\caption{Figure 11a,b. Basic movements: discrete step in (x,y) space, rotation, increase or decrease scale.}
\end{figure}

@@

\caption{Figure 12. The most basic drawing actions: dot, circle, line segment, arc.}
\end{figure}

@@

\caption{Figure 14. Paths: a key element of all vector graphics systems.  The actions are: start path, close and fill, close and don't fill, and terminate without closing.  All three are very useful.  Several actions exist to connect these, including cubic Bezier paths, arcs and line segments.  A very common source of errors in geometron glyphs is paths that are not closed.  Always close your paths. }
\end{figure}

@@

\caption{Figure 15. Square.  This figure is a closed path, so it has actions to both open the path and close it, separated by ``move along path'' actions, and rotations, which assume we are on a 90 degree symmetry.  A good exercise is to repeat this with 120 degree symmetry to get a triangle, with 72 degree to get a pentagon, and 60 degree symmetry to get a hexagon(these have more steps but are the same basic pattern.)}
\end{figure}

@@

\caption{Figure 16. Simple circles figure.  This figure, which is part of a Smith chart, is very simple to construct with just a few keystrokes in Geoemtron, and shows the power of this method for creating figures like this. }
\end{figure}

@@

\caption{Figure 17. Five pointed star.  Creating a five pointed star is also just a few keystrokes, with the right symmetry selected, and with start/stop of closed paths, one can make either a filled or unfilled star in seconds with Geometron.}
\end{figure}

@@

\caption{Figure 18. Cubic Bezier path which starts the construction of a inductor.  Note that with discrete Geometron-based actions, this is a much simpler task than with continuous vector graphics editors.  With no access to existing electronic data, one can reconstruct this on another computer just from reading the printed symbol glyphs in the proper order.}
\end{figure}

@@

\caption{Figure 19. An inductor built up from individual loop glyphs.}
\end{figure}

@@

\caption{Figure 20. Transformer made from same sub-elements as simple inductor.  Building circuits like this begins to show the labor-saving power of Geometron: this is just a few actions, but can now be encoded as a shape, so a single action can instance it, allowing the user to build up huge complex inductive circuits with very little effort or artistic skill. }
\end{figure}

@@

\caption{Figure 21. RLC resonator circuit.}
\end{figure}

@@

\caption{Figure 22. Quantum gate symbol construction and glyph spelling.}
\end{figure}

@@

\caption{Figure 23. Graph theory constructions using a Geometron instance of arrows and circles.}
\end{figure}

@@

\caption{Figure 24. Building a Feynman Diagram from individual sub-glyphs, with spelling shown below.}
\end{figure}

@@

First read this paper, focusing especially on the figures, and noting any errors or corrections to send to the author or further notes you want to add in your own documentation later.  Since this work is intended to build a collection of information which exists in the Commons, I as the author of this paper am asking for more help from you the reader than would be typical in a white paper like this. I hope that with your help, future revisions of this paper will be drastically improved as the software itself improves as well as the overall workflow and online documentation.  This whole paper is in the Public Domain and you are welcome to edit it and use it as you see fit, with or without attribution.

The graphics library can be found at www.quantumart.org/library.  Peruse it at your leisure, share it widely use it as needed.

@@

Hire me!

@@

\caption{Figure 25. Basic Geometron keyboard layout. Upper case letters on the rows QWERT, ASDF and ZXCV map to the shape table elements 0220-0227, 0230-237, and 0240-0247 respectively by default.  Re-mapping of the letters is carried out by changing the values in the Geometron Hypercube at the addresses from 040 through 0176, which is done by editing the file bytecode/keyboard.txt.}
\end{figure}

deep dive into code, improve it
get web developers to work over the CSS of your instance to brand it and make it fit with the rest of your web presence, build replicator with instructions for how to fork on your page. 
tell other people who will go back to step 1.

replication is covered in the next white paper.
applying the concepts of geometron to quantum information processing is covered in the third white paper, quantum modeling in HTML.

@@

point to the other two main white papers: 
    Self Replicating Graphical Social Network for QI and 
    Quantum Visualization and Control in HTML

    microblogging for real time technical graphical communication

    Building geometric languages to program quantum computers without the numerical/English based intermediary.

    Decentralized art feed network, I will help you replicate the code on your server, then adapt it for your specific applications, and train your people to use it, build custom keyboards, link to other nodes on Quantum AR

Creating direct connections between the web browser and geometry of Hilbert space, to cut out the ``middle man'' between a quantum user and quantum circuit.  Real time quantum controls.

    Create a language for protein structure using a custom GVM, another GVM for a many qubit hilbert space, then building a browser based UI for constructing purely geometric quantum algorithms which map problem space to hilbert space.

    GVM for Galois groups, geometrizing the problems of factorization so that people can develop new algorithms for factoring using GVM.

>>>>

\title{Geometron: A Geometric Language for Graphical Communication}
\author{Lafe Spietz}

@@

    Glyphs consist of sequences of actions.  They are expressed as strings in the form of base 8 addresses separated by commas, e.g. ``0300,0341,0333,0341,''.  Some addresses in the action cube consist of glyphs, which in turn reference other glyphs or actions.  Thus many levels of recursion are possible and used routinely.  This is a huge part of the power of this system over existing graphical systems like Adobe Illustrator.  Adding glyphs to the shape table and using those glyphs is not like just copying and pasting shapes in Illustrator.  It is in fact more like building up cell hierarchy in a electronic layout CAD program.

@@

\caption{Bottom Tablet.  This is split between the bottom part of the printable 7 bit ASCII code and various system actions which control things like cursor position while editing glyphs. }
\end{figure}

@@

\caption{Layers/colors.  These are at addresses 0320 through 0327.}
\end{figure}

@@

\caption{Basic movements: discrete step in (x,y) space, rotation, increase or decrease scale.}
\end{figure}

@@

\caption{The most basic drawing actions: dot, circle, line segment, arc.}
\end{figure}

@@

\caption{Paths: a key element of all vector graphics systems.  The actions are: start path, close and fill, close and don't fill, and terminate without closing.  All three are very useful.  Several actions exist to connect these, including cubic Bezier paths, arcs and line segments.  A very common source of errors in geometron glyphs is paths that are not closed.  Always close your paths. }
\end{figure}

@@

\caption{Square.  This figure is a closed path, so it has actions to both open the path and close it, separated by ``move along path'' actions, and rotations, which assume we are on a 90 degree symmetry.  A good exercise is to repeat this with 120 degree symmetry to get a triangle, with 72 degree to get a pentagon, and 60 degree symmetry to get a hexagon(these have more steps but are the same basic pattern.)}
\end{figure}

@@

\caption{Simple circles figure.  This figure, which is part of a Smith chart, is very simple to construct with just a few keystrokes in Geoemtron, and shows the power of this method for creating figures like this. }
\end{figure}

@@

\caption{Five pointed star.  Creating a five pointed star is also just a few keystrokes, with the right symmetry selected, and with start/stop of closed paths, one can make either a filled or unfilled star in seconds with Geometron.}
\end{figure}

@@

\caption{Cubic Bezier path which starts the construction of a inductor.  Note that with discrete Geometron-based actions, this is a much simpler task than with continuous vector graphics editors.  With no access to existing electronic data, one can reconstruct this on another computer just from reading the printed symbol glyphs in the proper order.}
\end{figure}

@@

\caption{An inductor built up from individual loop glyphs.}
\end{figure}

@@

\caption{Transformer made from same sub-elements as simple inductor.  Building circuits like this begins to show the labor-saving power of Geometron: this is just a few actions, but can now be encoded as a shape, so a single action can instance it, allowing the user to build up huge complex inductive circuits with very little effort or artistic skill. }
\end{figure}

@@

\caption{RLC resonator circuit.}
\end{figure}

@@

\caption{Quantum gate symbol construction and glyph spelling.}
\end{figure}

@@

\caption{Graph theory constructions using a Geometron instance of arrows and circles.}
\end{figure}

@@

\caption{Building a Feynman Diagram from individual sub-glyphs, with spelling shown below.}
\end{figure}

@@

First read this paper, focusing especially on the figures, and noting any errors or corrections to send to the author or further notes you want to add in your own documentation later.  Since this work is intended to build a collection of information which exists in the Commons, I as the author of this paper am asking for more help from you the reader than would be typical in a white paper like this. I hope that with your help, future revisions of this paper will be drastically improved as the software itself improves as well as the overall workflow and online documentation.  This whole paper is in the Public Domain and you are welcome to edit it and use it as you see fit, with or without attribution.  
The graphics library can be found at www.quantumart.org/library.  Peruse it at your leisure, share it widely use it as needed.

@@

@@

\caption{Standard Geometron keyboard layout. Upper case letters on the rows QWERT, ASDF and ZXCV map to the shape table elements 0220-0227, 0230-237, and 0240-0247 respectively by default.  Re-mapping of the letters is carried out by changing the values in the Geometron Hypercube at the addresses from 040 through 0176, which is done by editing the file bytecode/keyboard.txt.}
\end{figure}

@@
